---
title: "classes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{classes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fsmc)
```

# Classes inn `fsmc`

`fsmc` is built around a few classes which simplify common workflows with microbial communities. 

## MiCo

The `MiCo` class serves as the standard way to save and work with data on the metabolism of a microbial community. 

### Slots

- MO
- metabolites
- fluxes

### Functionality

Upon the creation of a `MiCo` class based on a three column input, additional information is calculated:

- neighbours
- binary matrix
- edges
- flux_consumption
- flux_production
- effective_flux_consumption
- effective_flux_production

## MiCoAl
The `MiCoAl` class serves as the standard way to align one or more `MiCo` objects. 

- Takes a number of `MiCo` objects as input (? list or ...) and an additional argument to specify if a pairwise alignment of the communities is desired. 
- The default is to align all communities against each other
- if `pairwise = TRUE` all unique pairwise combinations are aligned. 

### Methods

- cluster: Takes a `MiCoAl` object as input and an additional argument to specify the clustering algorithm to be used.
- only works on `MiCoAl` objects that have more than one alignment. 
