---
title: "Microbial Community Alignment Class"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Microbial-Community-Alignment-Class}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fsmc)
```




- Takes a number of `MiCo` objects as input (? list or ...) and an additional argument to specify if a pairwise alignment of the communities is desired. 
- The default is to align all communities against each other
- if `pairwise = TRUE` all unique pairwise combinations are aligned. 

### Methods

- cluster: Takes a `MiCoAl` object as input and an additional argument to specify the clustering algorithm to be used.
- only works on `MiCoAl` objects that have more than one alignment. 

### Identity
A value which gives a scalar value to represent the identity between two communities. 

$$ \frac{\alpha}{\sum\limits_{i = 1}^{n}(\sum C_i - \alpha) + \alpha} $$

