---
title: "MicrobiomeFunction Class"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MicrobiomeFunction Class}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fsmc)
```

## \code{MicrobiomeFunction} Class

The `MicrobiomeFunction` class serves as the standard way to save and work with data on the metabolism, the function, of a microbial community.

## Creation from data

To create an object of type `MiCo`, the user must input the data listed below. This data can either be contained in a single tibble or data frame, saved in a CSV file, or input as separate vectors.

- `species`: A character vector specifying the species present in the community.
- `met`: A character vector specifying the metabolites present in the community.
- `flux`: A numeric vector specifying the fluxes of each metabolite in the community.
- `name`: Character string giving the name of the community.

```{r}
s <- c("RQR9693L", "RQR9693L", "RQR9693L", "RQR9693L", "MEV1152G", "MEV1152G", "MEV1152G", "XIQ2234Q", "XIQ2234Q", "XIQ2234Q")
m <- c("met3", "met1", "met4", "met4", "met3", "met2", "met2", "met3", "met4", "met1")
f <- c(-0.3023640,  0.5344641, -2.2337716, 3.3063823, 2.5520278, 0.3388498, -1.8460633, -1.3043675, -0.4788769,  0.6027292)

newMiCo(species = s, metabolites = m, fluxes = f, name = "example_MiCo")
```

`fsmc` provides the function `syn_community()` to generate random `MiCo` objects based on user parameters. 

```{r}
makeSynMiCo(n_species = 8, max_met = 10, name = "example_syn_MiCo")
```

## Create a MiCo Object from a tibble
`fsmc` contains a set of example data that can be used for the analysis of microbial communities. For this example, we will use data created by [MiSoS(oup)](https://github.com/sirno/misosoup). Two example communities are provided in the package `ac_A1R12_1` and `cit_A1R12_1`.

The `MiCo` function can take either a path to a .csv file or a data frame/tibble as input.

## Contents

Upon the creation of a `MicrobiomeFunction` class based on a three column input, additional information is calculated:

- species
- metabolites
- fluxes
- edges
- binary matrix
- flux matrix 
- name
- flux_consumption
- flux_production
- effective_flux_consumption
- effective_flux_production

Each of these slots is described in the `MicrobiomeFunction-class()` class documentation.


## Methods 
- `getCo()`: Returns the community in tibble format.
- `getSpecies()`: Retrieves the species from a community.
- `getMet()`: Retrieves metabolites from a community.
- `getFlux()`: Retrieves the fluxes from a community.
- `getEdges()`: Retrieves the edges from a community.

