---
title: "Alignment of Communities on Different Substrates"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Alignment of Communities on Different Substrates}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

options(tibble.print_max = 10)
```

```{r setup}
library(dplyr)
library(fsmc)
library(magrittr)
library(purrr)
library(readr)
library(stringr)
library(tidyr)
```

# Alignment of Communities on Different Substrates


This vignette outlines a full workflow for the `fsmc` package. This includes the following steps:

- Community object creation
- Community alignment 
- Analysis of the alignment


The data analysed here was generated with `misosoup`, a command line tool designed to identify minimum viable communities in which each member is essential for the community to function. The data is provided in the `fsmc-data` repository on GitHub and can be used to test the package's functionality. 

The data set consists of 386 different microbial communities, including 272 with acetate as the carbon source, 219 with citrate as the carbon source, and 24 with fructose 6-phosphate (f6p) as the carbon source. 


```{r load-data}
sbs_url <- "https://raw.githubusercontent.com/admarhi/fsmc-data/main/misosoup/substrate.csv"

sbs_tb <- 
  read_csv(sbs_url) %>%
  group_by(substrate, focal_strain) %>% 
  filter(solution <= 5) %>% 
  ungroup() %>% 
  nest(.by = c("substrate", "focal_strain", "solution")) %>% 
  mutate(name = paste(substrate, focal_strain, solution, sep = "_")) %>% 
  select("name", "data")
```


```{r}
sbs_list <- set_names(sbs_tb$data, sbs_tb$name)
```


```{r create-MiCo}
ac <- 
  keep(sbs_list, str_starts(names(sbs_list), "ac")) %>%
  imap(newMiCo)

cit <- 
  keep(sbs_list, str_starts(names(sbs_list), "cit")) %>% 
  imap(newMiCo)

f6p <- 
  keep(sbs_list, str_starts(names(sbs_list), "f6p")) %>%
  imap(newMiCo)
```


```{r}
ac_alig <- newMiCoAl(ac)
cit_alig <- newMiCoAl(cit)
f6p_alig <- newMiCoAl(f6p)
```

```{r}
compareAlignments(
  ac_alig, cit_alig, f6p_alig,
  names = c("Acetate", "Citrate", "Fructose"),
  smooth = TRUE
) %>% plotly::ggplotly()
```


```{r}
plotAlignmentHeatmap(ac_alig, 0.5)
plotAlignmentHeatmap(cit_alig, 0.5)
plotAlignmentHeatmap(f6p_alig, 0.5)

plotAlignmentHeatmap(ac_alig, 0.8)
plotAlignmentHeatmap(cit_alig, 0.8)
plotAlignmentHeatmap(f6p_alig, 0.8)

plotAlignmentHeatmap(ac_alig, 0.88)
plotAlignmentHeatmap(cit_alig, 0.88)
plotAlignmentHeatmap(f6p_alig, 0.88)
```


```{r}
plotAlignmentNetwork(ac_alig, 0.5)
plotAlignmentNetwork(cit_alig, 0.5)
plotAlignmentNetwork(f6p_alig, 0.5)

plotAlignmentNetwork(ac_alig, 0.8)
plotAlignmentNetwork(cit_alig, 0.8)
plotAlignmentNetwork(f6p_alig, 0.8)

plotAlignmentNetwork(ac_alig, 0.95)
plotAlignmentNetwork(cit_alig, 0.95)
plotAlignmentNetwork(f6p_alig, 0.95)
```


