---
title: "Alignment of Cooperative and Competitive Communities"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Alignment of Cooperative and Competitive Communities}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(tibble.print_max = 10)
```

```{r setup}
library(dplyr)
library(fsmc)
library(tidyr)
library(purrr)
```


## Data
The set of competitve and cooperative communities both contain 100 communities. 

### Cooperative Communities

In the cooperative dataset there are 100 communities, made up from a total of 50 species. Each community consists of 10 species.

```{r}
coop_url <- "https://raw.githubusercontent.com/admarhi/fsmc-data/main/cooccurrence/cooperative.csv"
coop_tb <- readr::read_csv(coop_url)
```

```{r}
glimpse(coop_tb)

coop_tb %>% 
  group_by(community) %>% 
  summarise(n_species = length(unique(species)))
```

*Bacillus_humi_DSM_16318* is the only species that only acts as a donor, all 49 other species are both donors and receivers.

```{r}
coop_tb %>% 
  group_by(species) %>% 
  filter(all(fluxes > 0)) %>% 
  pull(species) %>% 
  unique()
```

#### Alignment 

Create `MiCo` objects from the data. 

```{r}
coop <- 
  coop_tb %>% 
  mutate(species = as.character(species)) %>% 
  nest(.by = community) %>% 
  pull(data) %>% 
  setNames(unique(coop_tb$community)) %>% 
  imap(~newMiCo(data = .x, name = .y))
```

Create an alignment of all cooperative communities.

```{r}
coop_alig <- newMiCoAl(coop)
```


### Competitive Communities

In the competitive dataset there are 50 species in total, with *Bacillus_humi_DSM_16318* being the only species that only acts as a donor, all 49 other species are both donors and receivers. 

```{r}
comp_url <- "https://raw.githubusercontent.com/admarhi/fsmc-data/main/cooccurrence/competitive.csv"
comp_tb <- readr::read_csv(comp_url)
```

```{r}
glimpse(comp_tb)

comp_tb %>% 
  group_by(community) %>% 
  summarise(n_species = length(unique(species)))
```



Create `MiCo` objects from the data. 

```{r}
comp <- 
  comp_tb %>% 
  rename(metabolites = "compound", fluxes = "flux") %>% 
  nest(.by = community) %>% 
  pull(data) %>% 
  setNames(unique(comp_tb$community)) %>% 
  imap(~newMiCo(data = .x, name = .y))
```

Create an alignment of all competitive communities.

```{r}
comp_alig <- newMiCoAl(comp)
```


## Alignment Comparison

The heatmaps below show metabolic functions that were aligned in at least `frac` of the communities. The metabolites on the y-axis are consumed to produce the metabolites on the x-axis. 

### Cooperative Communities 50%
```{r}
plotAlignmentHeatmap(coop_alig, frac = 0.5)
```

### Competitive Communities 50%
```{r}
plotAlignmentHeatmap(comp_alig, frac = 0.5)
```

### Cooperative Communities 80%
```{r}
plotAlignmentHeatmap(coop_alig, frac = 0.8)
```

### Competitive Communities 80%
```{r}
plotAlignmentHeatmap(comp_alig, frac = 0.8)
```

These results indicate that cooperative communities are functionally more similar to each other than competitive communities. With the minimum alignment set to 50% there is a great discrepancy between the extent of the alignment of cooperative and competitive communities. This becomes even more pronounced in the alignment >80%, here only the glycerol -> glycerol edge is present in competitive communities, while in the cooperative communities the production of hydrogen sulfide and ammonia from a variety of compounds are present.

We can use the `compareAlignments` function to compare the alignments and find values, at which the alignments contain the same number of reactions. 

```{r}
gg <- compareAlignments(
  coop_alig, comp_alig,
  names = c("cooperative", "competitive"))
gg
```

We can use `plotly` to make the plot interactive in order to easily find relevant values for further analysis. 

```{r}
plotly::ggplotly(gg)
```

From the interactive version of the plot we decide to compare alignments that align ~250 reactions in both, at a fraction of 0.51 (245 reactions) for cooperative and 0.31 (244 reactions) for competitive. The same for 130 reactions, 0.63 and 0.39 for cooperative and competitive respectively. 



### Comparison of alignments that share 30 reactions
```{r}
plotAlignmentHeatmap(coop_alig, 0.51)
plotAlignmentHeatmap(comp_alig, 0.31)
```

### Comparison of alignments that share 20 reactions
```{r}
plotAlignmentHeatmap(coop_alig, 0.63)
plotAlignmentHeatmap(comp_alig, 0.39)
```


### Comparison of alignments that share 20 reactions
```{r}
plotAlignmentHeatmap(comp_alig, 0.36)
plotAlignmentHeatmap(coop_alig, 0.6)
```
