---
title: "Example Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example-Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

```

```{r setup}
library(fsmc)
options(tibble.print_max = 10)
```


This vignette outlines an exemplary workflow for the `fsmc` package. The workflow will be broken down into the following steps:

- Community object creation
- Community alignment 
- Analysis of the alignment

## Create a MiCo Object
`fsmc` contains a set of example data that can be used for the analysis of microbial communities. For this example, we will use data created by [MiSoS(oup)](https://github.com/sirno/misosoup). Two example communities are provided in the package `ac_A1R12_1` and `cit_A1R12_1`.

The `MiCo` function can take either a path to a .csv file or a data frame/tibble as input.

```{r}
# Inspect the data 
ac_A1R12_1
cit_A1R12_1

# Create MiCo objects
mc1 <- MiCo(ac_A1R12_1)
mc2 <- MiCo(cit_A1R12_1)
mc3 <- MiCo(ac_A1R12_2)
mc4 <- MiCo(cit_A1R12_2)

# Inspect MiCo Objects
mc1
mc1
```

## Align MiCo Objects
Two `MiCo` objects can be aligned by creating a `MiCoAl` object. The `MiCoAl` creator function can take any number of `MiCo` objects as input.

```{r}
# Align the MiCo objects by creating a MiCoAl object
alignment <- MiCoAl(mc1, mc2, mc3, mc4)

# Inspect the alignment
alignment
```

### Analysis of the Alignment

```{r}

# alignmentNetwork(alignment, 0.8)
alignmentHeatmap(alignment, 0.2)

```

