---
title: "Experiment 1"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Experiment 1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

options(tibble.print_max = 10)

```

```{r setup}
library(fsmc)
library(stringr)
library(purrr)
```

# Experiment 1


This vignette outlines a full workflow for the `fsmc` package. This includes the following steps:

- Community object creation
- Community alignment 
- Analysis of the alignment

## Motivation

The data analysed here was generated with `misosoup`, a command line tool designed to identify minimum viable communities in which each member is essential for the community to function. The data is provide with the `fsmc` package and can be used to test its functionality. 

The data set consists of 56 different microbial consortia, including 26 with acetate as the carbon source, 26 with citrate as the carbon source, and 4 with fructose 6-phosphate (f6p) as the carbon source. 


## Analysis per Substrate
```{r}
### Could provide this in the data
ac <- keep(misosoup, str_starts(names(misosoup), "ac")) %>% imap(newMiCo)
cit <- keep(misosoup, str_starts(names(misosoup), "cit")) %>% imap(newMiCo)
f6p <- keep(misosoup, str_starts(names(misosoup), "f6p")) %>% imap(newMiCo)
```

```{r}
# discard beccause the only solution with this focal strain
ac <- discard(ac, names(ac) %in% "ac_A3R04_1")
```

```{r}
ac_alig <- newMiCoAl(ac)
cit_alig <- newMiCoAl(cit)
f6p_alig <- newMiCoAl(f6p)
```

```{r}
plotAlignmentHeatmap(ac_alig, 0.8)
plotAlignmentHeatmap(cit_alig, 0.8)
plotAlignmentHeatmap(f6p_alig, 0.5)
```
```{r}
plotAlignmentNetwork(ac_alig, 0.8)
plotAlignmentNetwork(cit_alig, 0.8)
plotAlignmentNetwork(f6p_alig, 0.5)
```




## Analysis per Focal Strain

Only A1R12 in two substrates.

```{r}
A1R12 <- keep(misosoup, str_detect(names(misosoup), "A1R12")) %>% imap(newMiCo)
A1R12_alig <- newMiCoAl(A1R12)
```

```{r}
plotAlignmentHeatmap(A1R12_alig, 0.8)
plotAlignmentHeatmap(A1R12_alig, 0.5)
plotAlignmentHeatmap(A1R12_alig, 0.2)
```


```{r}
plotAlignmentNetwork(A1R12_alig, 0.8)
plotAlignmentNetwork(A1R12_alig, 0.5)
plotAlignmentNetwork(A1R12_alig, 0.2)
```









### This can go in another vignette.
## Create a MiCo Object
`fsmc` contains a set of example data that can be used for the analysis of microbial communities. For this example, we will use data created by [MiSoS(oup)](https://github.com/sirno/misosoup). Two example communities are provided in the package `ac_A1R12_1` and `cit_A1R12_1`.

The `MiCo` function can take either a path to a .csv file or a data frame/tibble as input.


```{r}
# Inspect the data 
ac_A1R12_1
cit_A1R12_1

# Create MiCo objects
mc1 <- newMiCo(ac_A1R12_1)
mc2 <- newMiCo(cit_A1R12_1)
mc3 <- newMiCo(ac_A1R12_2)
mc4 <- newMiCo(cit_A1R12_2)

# Inspect MiCo Objects
mc1
mc1
```

## Align MiCo Objects
Two `MiCo` objects can be aligned by creating a `MiCoAl` object. The `MiCoAl` creator function can take any number of `MiCo` objects as input.

```{r}
# Align the MiCo objects by creating a MiCoAl object
alignment <- newMiCoAl(mc1, mc2, mc3, mc4)

# Inspect the alignment
alignment
```

### Analysis of the Alignment

```{r}

# alignmentNetwork(alignment, 0.8)
plotAlignmentHeatmap(alignment, 0.2)

```

