---
title: "ToDo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ToDo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fsmc)
```

# `fsmc` ToDo

## Improvements
- add fluxes to species edges
- Add warning if there are unexpected values in the diagonal (!=0)
- Throw insightful error when input wrong for MF


## New Methods
- Build and document the visualisation method for the alignment
- Function to identify critical/overlapping pathways 
- Create a wrapper function around MicrobiomeFunction that allows for easy import from relevant sources, including: SBML (Cobra CarveMe) JSON (COMETS, Escher) YAML (Misosoup). This needs to: accept factor variables for species and metabolite, allow for flexible variable naming, generate community name if missing
- Write set functions for all slots
- Write output methods to different formats


## General Ideas
- Can performance be improved by switching to use a databases?
- Reread hypergraph paper and consider implications


## Documentation
- Document the different types of input data from various sources such as FLYCOP, MisoSoup, etc.
  - What are the differences in the formats?
  - How can each be imported into fsmc?
  - Do standard formats exist?
  - Which formats should fsmc support in the future?
  - What does data from carvme look like? How does it differ from Misosoup/Flycop


## Long Term
- Chemical substitution score for metabolites