---
title: "Alignment of Communities with Different Functional Types"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Alignment of Communities with Different Functional Types}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

options(tibble.print_max = 10)
```

```{r setup}
library(dplyr)
library(fsmc)
library(magrittr)
library(purrr)
library(readr)
library(stringr)
library(tidyr)
```

selection <- c("A1R12", "B3M02", "3D05")
facilitation <- c("E3M17", "D2R05", "E3R18")


## Load Data 
```{r}
ft_url <- "https://raw.githubusercontent.com/admarhi/fsmc-data/main/misosoup/func_type.csv"

ft_tb <-
  read_csv(ft_url) %>%
  group_by(func_type, substrate, focal_strain) %>%
  filter(solution <= 2) %>%
  ungroup() %>%
  nest(.by = c("func_type", "substrate", "focal_strain", "solution")) %>%
  mutate(name = paste(substrate, focal_strain, solution, sep = "_"))
```

```{r}
selection_tb <- ft_tb %>%
  filter(func_type == "selection")

selection <-
  set_names(selection_tb$data, selection_tb$name) %>%
  imap(newMiCo)

facilitation_tb <- ft_tb %>%
  filter(func_type == "facilitation")

facilitation <-
  set_names(facilitation_tb$data, facilitation_tb$name) %>%
  imap(newMiCo)
```

```{r}
selection_alig <- newMiCoAl(selection)
facilitation_alig <- newMiCoAl(facilitation)
```


```{r}
plotAlignmentHeatmap(selection_alig, 0.5)
plotAlignmentHeatmap(facilitation_alig, 0.5)
```


```{r}
plotAlignmentHeatmap(selection_alig, 0.8)
plotAlignmentHeatmap(facilitation_alig, 0.8)
```

```{r}
plotAlignmentHeatmap(selection_alig, 0.95)
plotAlignmentHeatmap(facilitation_alig, 0.95)
```



```{r}
plotAlignmentNetwork(selection_alig, 0.5)
plotAlignmentNetwork(facilitation_alig, 0.5)

plotAlignmentNetwork(selection_alig, 0.8)
plotAlignmentNetwork(facilitation_alig, 0.8)

plotAlignmentNetwork(selection_alig, 0.95)
plotAlignmentNetwork(facilitation_alig, 0.95)
```




